### 2013-07-03 doc/dissertation/document/chapters/parallel_mc/parallel_mc.tex
adding more to the multiple sets analysis

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_pure_strong.pdf}
  \end{center}
  \caption{\textbf{Pure domain decomposition strong scaling absolute
      efficiency.}  \textit{Super-linear speed-up is from memory
      thrashing in the base case. MCLS is an order of magnitude slower
      arithmetically, causing the higher efficiency.}}
  \label{fig:titan_pure_strong}
\end{figure}

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_absolute.pdf}
  \end{center}
  \caption{\textbf{Pure domain decomposition weak scaling absolute
      efficiency.}}
  \label{fig:titan_weak_absolute}
\end{figure}

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_alg_eff.pdf}
  \end{center}
  \caption{\textbf{Pure domain decomposition weak scaling algorithmic
      efficiency.}}
  \label{fig:titan_weak_algorithmic}
\end{figure}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_implementation.pdf}
  \end{center}
  \caption{\textbf{Pure domain decomposition weak scaling
      implementation efficiency.}}
  \label{fig:titan_weak_implementation}
\end{figure}

@@

Given that overlap was not successful in boosting parallel
efficiencies, we next look to apply replication to the problem in the
form of multiple sets. Before performing parallel scaling studies
using multiple sets, several aspects of the replicated parallel
problem must be considered in order to effectively craft the studies
and interpret their results. First is the question of how many
stochastic histories to use to generate the correction vector in the
MCSA iteration. For this work we consider two choices, the split case
and the fully replicated case. As an example, consider a single set
problem where 20,000 histories are used in the Monte Carlo solve. If
we choose the split case, then solving the same problem with 2 sets
would give 10,000 histories in each set and 4 sets would give 5,000
histories in each set. Splitting the histories in this way provides
the same global number of histories used to compute the correction in
the single set problem. We expect to reduce the time to solution by
doing this as each individual set solve will occur faster in an almost
linear fashion with the reduced number of histories. For the
replicated history case, each additional set in the problem will use
just as many histories as the single set case. Using 2 sets with fully
replicated histories for our example problem then has each set
computing 20,000 histories with 40,000 global histories in the
computation. For the 4 set case, the number of global histories is
increased to 80,000. We also expect this type of replication to reduce
the time to solution as the extra global histories should reduce the
stochastic uncertainty in the correction vector and reduce the overall
number of MCSA iterations required to converge.

For the strong scaling study, we apply the additional sets as
follows. Using the same problems as the pure domain decomposition
scaling study, the multiple sets are used to replicate those problems
and boost the core count. For example, for the 4 set case, the data
point at 64 cores has the same $N/P$ ratio as the single set problem
with 16 cores. This is due to the fact that $N$ is fixed for the
strong scaling study and 4 replications gives a set size of 16
cores. For the 2 set case, the 32 core data point is solving the same
$N/P$ problem as the 16 core base case. In addition to considering the
replicated domain, we must also consider how to modify the
efficiencies we will compute. For the strong scaling case, recall that
the objective is to decrease the time to solution for a given global
problem size $N$ by increasing $P$. Therefore, we may use
Eqs~(\ref{eq:strong_scaling_absolute_ref}),
(\ref{eq:algorithmic_efficiency}), and
(\ref{eq:implementation_efficiency}) to compute the various strong
scaling efficiencies, but we must modify the reference computation in
each of these formulas to reflect our objective. For all efficiency
computations, the 16 core single set computation will be used as the
reference case. By adding more cores to the problem, either by
replicating with multiple sets, or decreasing the local problem size,
any computational resources added to the problem should aim to result
in speedup. If this speedup for one technique is less than another,
then that technique is deemed a less efficient use of those
computational resources.

For the multiple sets problem, the single set strong scaling study
from the pure domain decomposition base case was repeated for multiple
sets with both splitting of histories across sets and full replication
of histories across sets. Figure~\ref{fig:titan_strong_ms_time} gives
the actual wall times for these computations. There are two important
features to note in the wall time data. First, splitting the histories
amongst sets instead of replicating them is faster due to the fact
that cutting the number of histories in half reduces the time of an
iteration by a factor that is nearly linear while increasing linearly
the number of histories through replication does not decrease the
iterations required to converge by a linear factor. Second, until the
strong scaling wall is hit starting at around 10,000 cores, the single
set case actually perfoms the fastest with only marginal improvement in
runtimes at higher numbers of cores with more sets. At these larger
numbers of cores, however, the improvements are so modest that one is
better off running the same problem using a single set at lower core
counts to conserve computational resource while maintaining a good tim
to solution.

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_ms_time.pdf}
  \end{center}
  \caption{\textbf{Wall time in seconds to solution for each case for
      the strong scaling study with multiple sets.}}
  \label{fig:titan_strong_ms_time}
\end{figure}

From this timing data we then compute the absolute efficiencies for
strong scaling as given in Figure~\ref{fig:titan_strong_ms_eff}. As
observed in the timing data, because the single set case had the
fastest run times up to the strong scaling wall it also has the best
observed efficiencies. For the 2 set case with history splitting,
although the time to perform an iteration was nearly cut in half, the
extra parallel overhead associated with reducing the tally across the
blocks to combine the set results increases run times and reduces
efficiencies.This reduction across blocks is even more obvious for the
4 set case. For the replicated cases, we do observe a flat region of
parallel efficiencies at larger core counts (around 32,000 for the 4
set case with history replication), but the additional cores do not
reduce the runtime of the global problem efficiently. Ultimately, all
cases effectively hit the strong scaling wall at the same time. We
expect this if we consider the fact that adding sets to the problem is
in itself effectively a form of strong scaling. For any given problem
of fixed size $N$, adding extra sets to the computation decreases the
ratio of $N/P$ as $P$ will grow with the addition of sets. For the
split history case, the splitting further exacerbates this situation
by further decreasing the amount of histories that will be computed in
the local domain, giving a larger ratio of communication to work in
the Monte Carlo solve. As with with single set results, we also
observe some efficiencies greater than unity for the multiple set
cases also due to improved cache utilization.

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_ms_eff.pdf}
  \end{center}
  \caption{\textbf{Absolute parallel efficiency relative to 16-core
      1-set base case.}}
  \label{fig:titan_strong_ms_eff}
\end{figure}

Also of interest here is the effect of splitting histories amongst
sets versus replicating them on the iterative performance of the
method. Table~\ref{tab:ms_strong_alg_eff} gives the iterations
required to converge and computed algorithmic efficiences for each of
the cases presented in the scaling data. As expected, splitting
histories maintains a fixed global number of histories and therefore
maintained the number of iterations required to converge relative to
the single set base case. When histories were replicated, adding sets
decreased the number of iterations required to converge in a nonlinear
fashion. Using these algorithmic efficiencies, the implementation
efficiencies for the multiple set cases were computed and are given in
Figure~\ref{fig:titan_strong_ms_impeff}. From these results, we see
that the replicated history cases are even less efficient than in the
absolute case. Not only do we have the additional parallel overhead of
doing the block level reduction, but we also have additional histories
that increase the time to solution for a single iteration. Given that
the time to solution is not efficiently improved using multiple sets
in both the split and replicated history cases, multiple set domain
decomposition is not an effective means to boost the strong scaling
efficiencies of MCSA.

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_ms_impeff.pdf}
  \end{center}
  \caption{\textbf{Strong scaling implementation efficiency relative
      to the 16-core 1-set base case.}}
  \label{fig:titan_strong_ms_impeff}
\end{figure}

Next, we continue to a weak scaling study of the multiple sets
problem. As with the strong scaling study, we will modify the pure
domain decomposition study to account for the additional
replication. For each calculation in the single set study, that
problem will be replicated either 2 or 4 times with both split and
replicated histories to assess the effects on scalability and
runtime. Figure~\ref{fig:titan_weak_ms_time} gives the wall times from
the multiple sets weak scaling study. Of primary importance here is
the fact that adding sets to the problem with both split and
replicated histories actually decreases the time to solution. This was
not observed in the strong scaling case due to the larger decrease in
computational work as the number of cores was increased. This result
is significant in that it shows a solution technique in which the
linear problem can actually be replicated and enhance time to
solution, something that cannot be acheived with conventional
methods. At larger core counts, however, this reduction in compute
time is not as great as at lower core counts due to the fact that the
tally reduction across blocks requires more resources. In addition, at
over 130,000 cores for the largest 4 set computation, load balance is
likely becoming an issue due to the linear system and subsequent
parallel matrix and vector operations only occuring on a subset of the
entire processor space of the problem.

@@

For a multiple set analysis of the weak scaling timing results, we
again have to consider that adding sets to the problem is actually a
form of strong scaling. Consider a single set problem ($S=1$) for a
given $P$ and $N$. When that problem is now solved using 2 sets we
have $S=2$, $N$ and $2P$. For any number of sets we then have a global
problem size of $N$ while the number of processors is $SP$ where $P$
is the number of processors in the single set case. Therefore, $N/P$
is no longer fixed in the weak scaling study but rather $N/(SP)$ is
fixed. As a result, we modify the weak scaling absolute efficiency
relationship to account for this fact:
\begin{equation}
\eta_{weak}(M|N,P|Q,S) = \frac{T(M,Q)}{S \times T(N,P)}\:,
  \label{eq:ms_weak_efficiency}
\end{equation}
where now the absolute efficiency is a function of the number of sets
in the problem. Interestingly, Eq~(\ref{eq:ms_weak_efficiency}) has a
very similar form to the strong scaling efficiency given by
Eq~(\ref{eq:strong_scaling_absolute}), representative of the strong
scaling nature of adding additional sets. For problems where adding
sets improves time to solution, this new weak scaling formulation
accounts for how efficiently those extra resources are incorporated
into the problem. Without such a modification, the largest case run
for the split 4 set case would have a computed weak scaling efficiency
of nearly 100\% using the standard formula for absolute
efficiency. However, using 4 times as many cores as the single set
case increases the runtime for a fixed global problem size and
therefore we actually expect to compute a very low efficiency that
shows this very poor use of resources.

@@

As in the strong scaling case, splitting and replicating histories
across sets had effectively the same results for the weak scaling
study with the iterations to converge and compute algorithmic
efficienies given by Table~\ref{tab:ms_weak_alg_eff}. Again, when the
implementation efficiencies are computed, we see in
Figure~\ref{fig:titan_weak_ms_impeff} that splitting histories amongst
sets is still a more efficient manner of introducing multiple sets
rather than replicating histories in an attempt to reduce the number
of iterations required to converge.  Here we also note that this is
not a true weak scaling study as indicated by
Eq~(\ref{eq:ms_weak_efficiency}) but rather an odd combination of both
weak and strong scaling. Regardless of this, although multiple sets
are not the most efficient use of resources in this analysis, they do
enhance the time to solution through replication and do so
significantly at core counts of O(1,000) and lower. In both the weak
and strong scaling cases, due to the additional computational and
communication overhead of adding sets to the system, one should never
expect to boost parallel efficiencies for MCSA using this
technique. Further, in a purely strong scaling environment, no
performance gains should be expected as adding sets creates an even
more parasitic ratio of $N/P$. In a weak scaling environment, although
no efficiency increase will be noted, one can expect an enhancement of
time to convergence by replicating.

@@

>>>>

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_pure_strong.pdf}
  \end{center}
  \caption{\textbf{Pure domain decomposition strong scaling absolute
      efficiency.}  \textit{Super-linear speed-up is from memory
      thrashing in the base case. MCLS is an order of magnitude slower
      arithmetically, causing the higher efficiency. GMRES executes
      more operations than conjugate gradient, also creating a higher
      efficiency.}}
  \label{fig:titan_pure_strong}
\end{figure}

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_absolute.pdf}
  \end{center}
  \caption{\textbf{Pure domain decomposition weak scaling absolute
      efficiency.} \textit{MCLS is an order of magnitude slower
      arithmetically, causing the higher efficiency. GMRES executes
      more operations than conjugate gradient, also creating a higher
      efficiency.}}
  \label{fig:titan_weak_absolute}
\end{figure}

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_alg_eff.pdf}
  \end{center}
  \caption{\textbf{Pure domain decomposition weak scaling algorithmic
      efficiency.} \textit{As the global problem size was increased in
      the weak scaling study, both conjugate gradient and GMRES
      converged in fewer iterations, causing the rise in algorithmic
      efficiency.}}
  \label{fig:titan_weak_algorithmic}
\end{figure}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_implementation.pdf}
  \end{center}
  \caption{\textbf{Pure domain decomposition weak scaling
      implementation efficiency.} \textit{Considering the scalability
      of a single iteration of the implementation, the inflated
      efficiencies of the MCLS MCSA implementation become more
      obvious. Implementation optimization will likely reduce the MCSA
      values to a level more comparable to the Belos values.}}
  \label{fig:titan_weak_implementation}
\end{figure}

@@

Given that overlap was not successful in boosting parallel
efficiencies, we next look to apply replication to the problem in the
form of multiple sets. Before performing parallel scaling studies
using multiple sets, several aspects of the replicated parallel
problem must be considered in order to effectively craft the studies
and interpret their results. First is the question of how many
stochastic histories to use to generate the correction vector in the
MCSA iteration. For this work we consider two choices; the split case
and the fully replicated case. As an example these cases, consider a
single set problem where 20,000 histories are used in the Monte Carlo
solve. If we choose the split case, then solving the same problem with
2 sets would give 10,000 histories in each set and 4 sets would give
5,000 histories in each set. Splitting the histories in this way
provides the same global number of histories used to compute the
correction in the single set problem. We expect to reduce the time to
solution by doing this as each individual set solve will occur faster
in an almost linear fashion with the reduced number of histories. For
the replicated history case, each additional set in the problem will
use just as many histories as the single set case. Using 2 sets with
fully replicated histories for our example problem then has each set
computing 20,000 histories with 40,000 global histories in the
computation. For the 4 set case, the number of global histories is
increased to 80,000. We also expect this type of replication to reduce
the time to solution as the extra global histories should reduce the
stochastic uncertainty in the correction vector and reduce the overall
number of MCSA iterations required to converge.

\subsubsection{Strong Scaling with Multiple Sets}
\label{subsubsec:ms_strong}

For the strong scaling study, we apply the additional sets as
follows. Using the same problems as the pure domain decomposition
scaling study, the multiple sets are used to replicate those problems
and boost the core count. For example, for the 4 set case, the data
point at 64 cores has the same $N/P$ ratio in one set as the single
set problem with 16 cores. This is due to the fact that $N$ is fixed
for the strong scaling study and 4 replications gives a set size of 16
cores. For the 2 set case, the 32 core data point is solving the same
$N/P$ problem in a set as the 16 core base case.

In addition to considering the replicated domain, we must also
consider how to modify the efficiencies we will compute. For the
strong scaling case, recall that the objective is to decrease the time
to solution for a given global problem size $N$ by increasing
$P$. Therefore, we may use Eqs~(\ref{eq:strong_scaling_absolute_ref}),
(\ref{eq:algorithmic_efficiency}), and
(\ref{eq:implementation_efficiency}) to compute the various strong
scaling efficiencies, but we must modify the reference computation in
each of these formulas to reflect our objective. For all efficiency
computations, the 16 core single set computation will be used as the
reference case. By adding more cores to the problem, either by
replicating with multiple sets, or decreasing the local problem size,
any computational resources added to the problem should aim to result
in speedup of this reference case. If this speedup for one technique
of adding cores is less than another, then that technique is deemed a
less efficient use of those computational resources.

For the multiple sets problem, the single set strong scaling study
from the pure domain decomposition base case was repeated for multiple
sets with both splitting of histories across sets and full replication
of histories across sets using both 2 and 4
sets. Figure~\ref{fig:titan_strong_ms_time} gives the actual wall
times for these computations. There are two important features to note
in the wall time data. First, splitting the histories amongst sets
instead of replicating them is faster due to the fact that cutting the
number of histories in half reduces the time of an iteration by a
factor that is nearly linear while increasing linearly the number of
histories through replication does not decrease the iterations
required to converge by a linear factor. Second, until the strong
scaling wall is hit starting at around 10,000 cores, the single set
case actually perfoms the fastest with only marginal improvement in
runtimes at higher numbers of cores with more sets. At these larger
numbers of cores, however, the improvements are so modest that one is
better off running the same problem using a single set at lower core
counts to conserve computational resources while maintaining a good
time to solution.

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_ms_time.pdf}
  \end{center}
  \caption{\textbf{Wall time in seconds to solution for each case for
      the strong scaling study with multiple sets.} \textit{Until the
      strong scaling wall is reached at O(10,000) cores, the single
      set case performs the best. For the multiple set cases, it is
      faster to split histories amongst sets and maintain iterative
      performance rather than replicate histories to improve iterative
      performance.}}
  \label{fig:titan_strong_ms_time}
\end{figure}

From this timing data we then compute the absolute efficiencies for
strong scaling as given in Figure~\ref{fig:titan_strong_ms_eff} using
the 16-core single set calculation as the reference case. As observed
in the timing data, because the single set case had the fastest run
times up to the strong scaling wall it also has the best observed
efficiencies. For the 2 set case with history splitting, although the
time to perform an iteration was nearly cut in half, the extra
parallel overhead associated with reducing the tally across the blocks
to combine the set results increases run times and reduces
efficiencies. This reduction across blocks is even more obvious for
the 4 set case. For the replicated cases, we do observe a flat region
of parallel efficiencies at larger core counts (up to around 32,000
for the 4 set case with history replication) showing improved scaling
within context of not considering the single set
calculation. Unfortunately, the additional cores do not reduce the
runtime of the global problem as efficiently as expected. Ultimately,
all cases effectively hit the strong scaling wall at the same time at
around O(10,000) cores.

We expect this if we consider the fact that adding sets to the problem
is in itself effectively a form of strong scaling. For any given
problem of fixed size $N$, adding extra sets to the computation
decreases the global ratio of $N/P$ as $P$ will grow with the addition
of sets (although $N/P$ is constant within a set). For the split
history case, the splitting further exacerbates this situation by
further decreasing the amount of histories that will be computed in
the local domain, giving a larger ratio of communication to work in
the Monte Carlo solve. As with with single set results, we also
observe some efficiencies greater than unity for the multiple set
cases also due to improved cache utilization.

Although not as dramatic as one might originally expect from
introducing replication, there are some modest gains in efficiencies
at high core counts by using multiple sets. Of interest here is where
the multiple set cases perform better than the single set case after
the single set case has hit the strong scaling wall. In
Figure~\ref{fig:titan_strong_ms_eff}, at 16,384 cores the single set
case operates at 38\% efficiency while at the same number of cores,
the 2 set case with history replication operates at 62\%
efficiency. This is reasonable improvement in the use of those
computational resources, gained by replicating the problem. Beyond
16,384 cores, there is not a compelling reason to use more
computational resources for the this problem.

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_ms_eff.pdf}
  \end{center}
  \caption{\textbf{Multiple set absolute parallel efficiency.}
    \textit{Computed relative to the 16-core 1-set base case. Using a
      single set is the best means by which to improve strong scaling
      up to the strong scaling wall. At higher core counts past where
      the single set case hits the strong scaling wall adding sets can
      provide some improvements in efficiencies.}}
  \label{fig:titan_strong_ms_eff}
\end{figure}

Also of interest here is the effect of splitting histories amongst
sets versus replicating them on the iterative performance of the
method. Table~\ref{tab:ms_strong_alg_eff} gives the iterations
required to converge and computed algorithmic efficiences for each of
the cases presented in the strong scaling data. As expected, splitting
histories maintains a fixed global number of histories and therefore
maintained the number of iterations required to converge relative to
the single set base case. When histories were replicated, adding sets
decreased the number of iterations required to converge in a nonlinear
fashion. Using these algorithmic efficiencies, the implementation
efficiencies for the multiple set cases were computed and are given in
Figure~\ref{fig:titan_strong_ms_impeff}. From these results, we see
that the replicated history cases are even less efficient than in the
absolute case. Not only do we have the additional parallel overhead of
doing the block level reduction, but we also have additional histories
that increase the time to solution for a single iteration.

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_ms_impeff.pdf}
  \end{center}
  \caption{\textbf{Multiple set strong scaling implementation
      efficiency.} \textit{Computed relative to the 16-core 1-set base
      case. Considering iterations required to converge, the
      performance of the split history cases at much better than the
      cases with history replication.}}
  \label{fig:titan_strong_ms_impeff}
\end{figure}

\subsubsection{Weak Scaling with Multiple Sets}
\label{subsubsec:ms_weak}

Next, we continue to a weak scaling study of the multiple sets
problem. In the same way as the strong scaling study, we will modify
the pure domain decomposition study to account for the additional
replication. For each calculation in the single set study, that
problem will be replicated either 2 or 4 times with both split and
replicated histories to assess the effects on scalability and
runtime. Figure~\ref{fig:titan_weak_ms_time} gives the wall times from
the multiple sets weak scaling study. Of primary importance here is
the fact that adding sets to the problem with both split and
replicated histories actually decreases the time to solution. This was
not observed in the strong scaling case until much larger core counts
due as the multiple set computations hit the strong scaling wall after
the single set computation.

This result is significant in that it shows a solution technique in
which the linear problem can actually be replicated and enhance time
to solution, something that cannot be acheived with conventional
methods. At larger core counts, however, this reduction in compute
time is not as large as at lower core counts due to the fact that the
tally reduction across blocks requires more resources and those
resources are clearly growing with core count (most obviously in the 4
set case with split histories). In addition, at 131,072 cores for the
largest 4 set computation, load balance is likely becoming an issue
due to the linear system and subsequent parallel matrix and vector
operations only occuring on a subset of the entire processor space of
the problem while the Monte Carlo calculation is occuring on all
processors.

@@

For a multiple set analysis of the weak scaling timing results, we
again have to consider that adding sets to the problem is actually a
form of strong scaling. Consider a single set problem ($S=1$) for a
given $P$ and $N$. When that problem is now solved using 2 sets we
have $S=2$, $N$ and $2P$. For any number of sets we then have a global
problem size of $N$ while the number of processors is $SP$ where $P$
is the number of processors in the single set case. Therefore, $N/P$
is no longer fixed in the weak scaling study but rather $N/(SP)$ is
fixed. As a result, we modify the weak scaling absolute efficiency
relationship to account for this fact:
\begin{equation}
\eta_{weak}(M|N,P|Q,S) = \frac{T(M,Q)}{S \times T(N,P)}\:,
  \label{eq:ms_weak_efficiency}
\end{equation}
where now the absolute efficiency is a function of the number of sets
in the problem and again $M/Q = N/P$. As with the strong scaling
study, we will use the 16-core single set case as the reference
computation for efficiencies. Interestingly,
Eq~(\ref{eq:ms_weak_efficiency}) has a very similar form to the strong
scaling efficiency given by Eq~(\ref{eq:strong_scaling_absolute}),
representative of the strong scaling nature of adding additional
sets. For problems where adding sets improves time to solution, this
new weak scaling formulation accounts for how efficiently those extra
resources are incorporated into the problem. Without such a
modification, the largest case run for the split 4 set case would have
a computed weak scaling efficiency of nearly 100\% using the standard
formula for absolute efficiency. However, using 4 times as many cores
as the single set case increased the runtime for a fixed global
problem size and therefore we would actually expect to compute a very
low efficiency that shows this very poor use of resources.

@@

As in the strong scaling case, splitting and replicating histories
across sets had effectively the same results for the weak scaling
study with the iterations to converge and computed algorithmic
efficiencies given by Table~\ref{tab:ms_weak_alg_eff}. Again, when the
implementation efficiencies are computed, we see in
Figure~\ref{fig:titan_weak_ms_impeff} that splitting histories amongst
sets is still a more efficient manner of introducing multiple sets
rather than replicating histories in an attempt to reduce the number
of iterations required to converge.  Here we also note that this is
not a true weak scaling study as indicated by
Eq~(\ref{eq:ms_weak_efficiency}) but rather an odd combination of both
weak and strong scaling. Regardless of this, although multiple sets
are not the most efficient use of resources in this analysis, they do
enhance the time to solution through replication and do so
significantly at core counts of O(1,000) and lower. In both the weak
and strong scaling cases, due to the additional computational and
communication overhead of adding sets to the system, one should never
expect to seriously boost parallel efficiencies for MCSA using this
technique accept for certain instances past the strong scaling wall in
a purely strong scaling environment. In a weak scaling environment,
although no efficiency increase will be noted, one can expect an
enhancement of time to convergence by replicating.

@@

Based on the analysis of the pure domain decomposed MCSA algorithm and
subsequently the MSOD implementation, one may ask then ask if there is
any need to commincate histories from domain-to-domain at all. Overlap
was not successful because so few histories needed to be communicated
in the first place that keeping them on-process resulted in more work
than the communications savings that occurred. If that is true, then
perhaps without any overlap or communication, just doing local Monte
Carlo may be satisfactory for accelerating the MCSA iteration.
